Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-25 paper/paper.tex
finished edits up to the end of Knight Two subsubsection

At the time of this writing, we have completed and flown a single flight vehicle, which we have named the \emph{Daedalus}.
We have also nearly completed a very similar backup airframe which serve as a backup in case the \emph{Daedalus} has a disaster. The \emph{Knight Two} will be fitted with nearly identical R/C flight electronics, and accept the same autopilot and imaging system payload as the \emph{Daedalus}.

@@

We elected to pursue a kit-type airplane rather than our own design. 
Our own custom design, the \emph{Icarus}, suffered a catastrophic structural failure last year. From this, we learned that custom structures require much more testing and revision than a proven kit. We also reconsidered our payload requirements and decided we could easily modify a kit plane to accept our autopilot and imaging system.

\subsubsection{Daedalus}
\begin{wrapfigure}{l}{0.4\textwidth}
	\includegraphics[width=0.37\textwidth]{../images/daedalus_isometric.jpg}
	\caption{The \emph{Daedalus}}
	\label{fig:daedalus}
\end{wrapfigure}
A member of our local R/C club, Tri-County RC \cite{tricountyRC}, donated a ten-foot wingspan high wing trainer to our club. The plane, first built out of foam and balsa from long-lost plans in 1986, was accepted graciously, but required quite a bit of work before it was once again flight-worthy. We removed the covering to find water damage and rot which resulted from years of storage. We stripped and rebuilt nearly the entire airframe, adding carbon-fiber reinforcements to the wing in anticipation of increased wing loading due to our payload. Once rebuilt and covered, we tested the \emph{Daedalus} weighed 19.5 lbs with engine. A full 24oz fuel tank, plus 3.5 lbs electronics payload, would bring the maximum takeoff weight to 25.5lbs.

We wanted to certify the wings and wing root would withstand large dynamic forces in flight. 
We designed a test similar to mimic the 
Federal Airworthiness Standards' structural requirements\footnote{Special Federal Aviation Regulation No. 23, Subpart C--Structure. Assuming full load on wing as described in 23.335 paragraph 4.i., where an aircraft must pull out of a \degrees{7.5} dive at cruise velocity and cruise power ``with a load factor of 1.5 (0.5$g$. acceleration increment)'' \cite{far23}}. Our first test was designed to certify that the wing, supported at the wing root and fuselage, could take a bottom loading present in a 1.5$g$ acceleration, with a safety factor of 1.5\footnote{As stated in 23.303 \cite{far23}.}.

@@

Satisfied, made engine and surface tests (see \ref{sec:appendix_preflight}) before taxiing the plane around a parking lot.  We brought the plane back inside, examined it for signs of stress and, finding everything in good condition, deemed the \emph{Daedalus} flight-worthy.

@@

In order to mitigate a disaster such as we had last year, we decided to build another airframe which could replace the \emph{Daedalus} at short notice. We selected an Aero-Design 12 Foot Telemaster \cite{aerodesign} because it was available as a balsa kit and similar in size to the \emph{Daedalus}.

We named it the \emph{Knight Two} after the Rutgers University mascot, the Scarlet Knight. We may rename it if someone can think of a better name. Pat needed to think up a decent name real fast in order to make this rough draft.

Since our testing plan for the \emph{Daedalus} was successful, we will follow the same plan when, in the coming weeks, we finish building \emph{Knight Two}.

Someone please detail the outer dimensions. The inner dimensions, space used for flight electronics, space used for payload underneath. Landing gear height. Number of servos and their locations

Figure may go here: Line drawing of Knight Two. JOHN

>>>>

At the time of this writing, we have completed and flown a single flight vehicle, which we have named the \emph{Daedalus}.
We have also nearly completed a very similar backup airframe which will serve as a backup in case the \emph{Daedalus} has a disaster. The \emph{Knight Two} will be fitted with nearly identical R/C flight electronics, and accept the same autopilot and imaging system payload as the \emph{Daedalus}.

@@

\subsubsection{Daedalus}
\begin{wrapfigure}{l}{0.4\textwidth}
	\includegraphics[width=0.37\textwidth]{../images/daedalus_isometric.jpg}
	\caption{The \emph{Daedalus}}
	\label{fig:daedalus}
\end{wrapfigure}
Louis Stumpf, a member of our local R/C club, donated a 10ft 1in (3.07m) wingspan, 7ft 8in (2.33m) long, high wing trainer to our club. It met all of the requirements outlined previously.

The plane, first built out of foam and balsa from long-lost plans in 1986, was accepted graciously, but required quite a bit of work before it was once again flight-worthy. We removed the covering to find water damage and rot which resulted from years of storage. We stripped and rebuilt nearly the entire airframe, adding carbon-fiber reinforcements to the wing in anticipation of increased wing loading due to our payload. Once rebuilt and covered,  the \emph{Daedalus} weighed 19.5 lbs with engine. A full 24oz fuel tank, plus 3.5 lbs electronics payload, would bring the maximum takeoff weight to 25.5lbs.

We wanted to certify the wings and wing root would withstand large dynamic forces in flight. 
We designed a test to mimic the 
Federal Airworthiness Standards' structural requirements\footnote{Special Federal Aviation Regulation No. 23, Subpart C--Structure. Assuming full load on wing as described in 23.335 paragraph 4.i., where an aircraft must pull out of a \degrees{7.5} dive at cruise velocity and cruise power ``with a load factor of 1.5 (0.5$g$. acceleration increment)'' \cite{far23}}. Our first test was designed to certify that the wing, supported at the wing root and fuselage, could take a bottom loading present in a 1.5$g$ acceleration, with a safety factor of 1.5\footnote{As stated in 23.303 \cite{far23}.}.

@@

Satisfied, we made engine and surface tests (see \ref{sec:appendix_preflight}) before taxiing the plane around a parking lot.  We brought the plane back inside, examined it for signs of stress and, finding everything in good condition, deemed the \emph{Daedalus} flight-worthy.

@@

In order to mitigate a disaster such as we had last year, we decided to build another airframe which could replace the \emph{Daedalus} at short notice. We selected an Aero-Design 12 Foot Telemaster \cite{aerodesign} because it was available as a balsa kit and similar in size to the \emph{Daedalus}. The 12 Foot Telemaster has a 12ft 1in (3.68m) wingspan, and is 7ft 10in (2.38m) in length.We named it the \emph{Knight Two} after the Rutgers University mascot, the Scarlet Knight.

At the time of this writing, the \emph{Knight Two} is 85\% complete. We plan to complete the aircraft and bring it to the competition as a spare.  
Since our testing plan for the \emph{Daedalus} was successful, we will follow the same plan when the \emph{Knight Two} is completed.
